FictionEro - Affective Impact of Fiction

### 2025-09-29 analysis/analysis.qmd
started change to brms

table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
    gt::fmt_auto()
}

g1 <- modelbased::estimate_grouplevel(arousal1)
table_dvour(g1)

@@

```{r}
g2 <- modelbased::estimate_grouplevel(arousal2)
table_dvour(g2)
```

### Participant effects

>>>>

model_draft <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (1|Item),
                          data=df2,
                          family=glmmTMB::ordbeta(),
                          control = glmmTMB::glmmTMBControl(parallel = 8))

```
### Reliability

```{r}
table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = c("red","green"), domain = c(0, 1)) |> 
    gt::fmt_auto()
}

g1 <- modelbased::estimate_grouplevel(model_draft)
table_dvour(g1)

@@

#### Participant effects

```{r}
colors <- c("(Intercept)" = "#9C27B0","ConditionAI-Generated" = "#FF9800")

p2_dvour <- g1 |> 
  ggplot(aes(x = Coefficient, y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```

### Correlation
